Project Proposal

### 2024-11-18 NFL_IDS702Projectproposal.qmd
change plot size

```{r load-packages, message = FALSE, warning = FALSE}
library(dplyr)
```

@@

ggpairs(
  nfldata_1_viz,
  columns = c("dropbackCategory", "dropbackDistance" ),
  aes(color = as.factor(passResult)), # Treat passResult as a factor
  upper = list(continuous = "points"),
  lower = list(continuous = "points")
) +
  labs(
    title = "Pairwise Plots of Predictors Colored by Pass Result",
    color = "Pass Result"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

>>>>

```{r load-packages, message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(GGally)
```

@@

ggpairs(
  nfldata_1_viz,
  columns = c("dropbackCategory", "dropbackDistance", "timeToThrow", "passLength"),
  aes(color = as.factor(passResult)), # Treat passResult as a factor
  upper = list(continuous =  wrap("points", size = 0.3)),
  lower = list(continuous =  wrap("points", size = 0.3))
) +
  labs(
    title = "Pairwise Plots of Predictors Colored by Pass Result",
    x = "Predictor 1",
    y = "Predictor 2",
    color = "Pass Result"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    axis.text.x = element_text(size = 3.5),  # Adjust x-axis text size
    axis.text.y = element_text(size = 8),  # Adjust y-axis text size
    axis.ticks.x = element_blank(),       # Remove excess x-axis ticks
    axis.ticks.y = element_blank()        # Remove excess y-axis ticks
  )
